Borel regularity for ODEs and thimble integrals

### 2023-08-02 exp-resurgence.tex
exp-resurgence: cleaning the introduction, the statements of the theorems, and some references.
Change the notation of the example in the introduction, in fact, it didn't match the dlmf and Mathematica conventions. 

Removing hold version in proof of main results. 

Add pictures for thimbles.

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
\begin{equation}
e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples. As another example, you might rewrite the integral
\begin{verify}
    \[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
\end{verify}

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
as
% see expansion.sage
\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.

\begin{verify}
    \begin{align*}
& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
\end{align*}
\end{verify}

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. \textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

@@

%\color{gray}
%\begin{itemize}
%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
%\begin{itemize}
%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
%\item Feynman diagram series?
%\end{itemize}
%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
%\begin{itemize}
%\item \done{Borel summation work in three steps. First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
%\item {[Draw the square!]}
%\end{itemize}
%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
%\item In many cases, it picks correctly, producing an actual solution to your problem.
%\begin{itemize}
%\item The question of how that happens is the starting point for this paper.
%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$. For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
%\end{itemize}
%\end{itemize}
%\color{black}
\subsection{A new perspective: Borel regularity}
\subsubsection{Introducing Borel regularity}
\begin{itemize}
\item Start instead with a holomorphic solution $\Phi$.
\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
\end{itemize}
%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e. $|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).

We'll restrict our attention to the case where the roots of $P$ are distinct.

The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.

\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}

@@

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). Conversely, we can explicitly build a distinguished basis of analytic solutions:

\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with

\begin{equation}
\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
\textcolor{red}{${\psi}_j=\zeta_j^{-\tau_j-1}+f_{j,\star}$} and $f_{j,\star}\in\singexpalg{\tau_j-1}(\Omega_j)$ for an open star-shaped domain $\Omega_j$ which avoids the other critical points (see the definition in Section \ref{setting-ODE}).
\end{theorem}

@@

\begin{theorem}\label{thm2}
For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta}$ for some direction $\theta$.
Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}

@@

In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).

The key step is then comparing $\psi_j$ and $\hat{\psi}_j$. First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too. In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
therefore, by our uniqueness result~\ref{thm1}, we conclude that $\psi_j$ and $\hat{\psi}_j$ must coincide up to scaling by a constant.

As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$. Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.

@@

\color{Tan}
\begin{remark}
Although, in our proof, we use $1$-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane). \textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability? For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$? Check carefully the argument of multi-summability]} 
\end{remark}

\color{magenta}
[Veronica]

Although, in our proof, we adapt an argument by M. Loday-Richaud and P. Remy (see \S 2 in\cite{loday-Remy2011}) to guarantee Borel--Laplace summability, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane). In addition, our proof stresses the importance of the position domain, where in fact the crucial step of the proof is done.

@@

We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries. We follow \cite{pham} and $\S 1$ in \cite{Arnold}. Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define 
\begin{align*}
    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
\end{align*}
and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t. } \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}. Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$. This leads to further identifications:

@@

Then we recall the definition of $H_{dR,z}^\cdot$: it is the hypercohomolgy of the twisted de Rham complex

@@

As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$). The jumps can be described geometrically using the theory of Picard--Lefschetz. Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.

Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).

@@

These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22},Berry and Howls \cite{berry1991hyperasymptotics}, Delabere and Pham \cite{Delabaere-Pham99}, Dunne and Unsal \cite{dunne-unsal}, and others. \textcolor{orange}{[add references]}

@@

As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}). Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.

>>>>

\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{85085}{33592320} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
\color{orange}
\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
\color{black}
Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}. \textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series? Hopefully it wouldn't be too hard, but it would be a pain.]}
\begin{defn}
On an open sector $\Omega$ around $\infty$, a power series
\begin{equation}\label{series:asymp-defn}
\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$.

@@

%\color{gray}
%\begin{itemize}
%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
%\begin{itemize}
%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
%\item Feynman diagram series?
%\end{itemize}
%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
%\begin{itemize}
%\item \done{Borel summation work in three steps. First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$. By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
%\item {[Draw the square!]}
%\end{itemize}
%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
%\item In many cases, it picks correctly, producing an actual solution to your problem.
%\begin{itemize}
%\item The question of how that happens is the starting point for this paper.
%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$. For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
%\end{itemize}
%\end{itemize}
%\color{black}
\subsection{A new perspective: Borel regularity}
\subsubsection{Introducing Borel regularity}
We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.

%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).

The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.

\item the second problem is evaluating a certain kind of integral: a one-dimensional {\em thimble integral}

@@

However, can we find a distinguished basis for solutions in a purely analytic way? This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$. In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}). Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form

\begin{equation}
\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
\end{equation}

labeled by the roots of $P$. This type of operators are the one we studied in {\tt reg-sing-volterra}, hence we know there exists a unique solution $\psi_j=f_{j,0}+f_{j,\star}$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and $f_{j,\star}\in\singexpalg{\tau_j}(\Omega_j)$ for an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}). In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}$.

\begin{theorem}\label{thm1}
    The holomoprhic functions $\Psi_j$ are solutions of $\mathcal{P}\Psi_j=0$. In particular, they are a frame of analytic solutions.
\end{theorem}

@@

\begin{theorem}\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}

@@

In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 {\tt reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (Theorem \ref{thm1}).

The key step is then comparing $\psi_j$ and $\hat{\psi}_j$. First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE). In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
therefore, by our uniqueness result, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant. Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.

As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$. Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.

@@

\begin{remark}
The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namley, drawing the red arrow of the diagram). This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE. However, the approach of Borel regularity is different as it is based on the analytic solution in the position domain. 
\end{remark}

@@

We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries. We follow \cite{pham} and \cite[Section 1]{Arnold}. Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define 
\begin{align*}
    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
\end{align*}
and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t. } \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}. Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$. This leads to further identifications:

@@

Then we recall the definition of $H_{dR,z}^*$: it is the hypercohomolgy of the twisted de Rham complex

@@

As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$). The jumps can be described geometrically using the theory of Picard--Lefschetz. Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies. We will discuss this phenomena from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions. \textcolor{orange}{[Can we comment more about this? For instance as a consequence of Theorem 3.3]}

Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).

@@

These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[Delabere \& Howls, Howls, Dingle]}.

@@

As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}). Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain. We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain. In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem 4 in {\tt reg-sing-volterra}). Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.
